Turbulence in compact to giant H~II regions

### 2022-12-20 strucfunc_paper.tex
Javier changes before submission

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García Vázquez et al.]{
  J. García Vázquez$^{1}$\thanks{
    E-mail: \href{mailto:jgarciav1600@alumno.ipn.mx}{jgarciav1600@alumno.ipn.mx}
  },
  William J. Henney$^{2}$
  and H. O. Castañeda$^{1}$\thanks{Deceased.}
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México C.P. 07738\\
$^{2}$Instituto de Radioastronomía y Astrofísica,
Universidad Nacional Autónoma de México,
Antigua Carretera a Pátzcuaro \#8701,\\
Ex-Hda. San José de la Huerta, 
Morelia, Michoacán, México C.P. 58089\\
}

@@

\subsection{Comparison with previous structure functions}
\label{sec:comp-with-prev}
Comparison with prior studies is complicated by the
diversity of methodologies that  have been employed.
There is almost universal agreement on how to measure
the velocity variance \(\sigma^2\pos\),
although even here there can be small differences according
to whether the centroid velocities come from gaussian fitting
or velocity moments,
and whether or not smooth large-scale trends are first removed.
\citet{arthur2016turbulence} compared multiple studies of the
inner Orion Nebula, finding agreement to within 20\%
in \(\sigma^2\pos\) determinations
for emission lines that trace the bulk of the fully ionized gas.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García Vázquez et al.]{
  J. García Vázquez$^{1}$\thanks{
    E-mail: \href{mailto:jgarciav1600@alumno.ipn.mx}{jgarciav1600@alumno.ipn.mx}
  },
  William J. Henney$^{2}$
  and H. O. Castañeda$^{1}$\thanks{Deceased.}
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, U.P. Adolfo López Mateos, Zacatenco, Ciudad de México, México C.P. 07738\\
$^{2}$Instituto de Radioastronomía y Astrofísica,
Universidad Nacional Autónoma de México,
Antigua Carretera a Pátzcuaro \#8701,\\
Ex-Hda. San José de la Huerta, 
Morelia, Michoacán, México C.P. 58089\\
}

@@

\subsection{Comparison with previous structure functions}
\label{sec:comp-with-prev}
Comparison with prior studies is complicated by the
diversity of methodologies that  have been employed.
There is almost universal agreement on how to measure
the velocity variance \(\sigma^2\pos\),
although even here there can be small differences according
to whether the centroid velocities come from gaussian fitting
or velocity moments,
and whether or not smooth large-scale trends are first removed.
Also, the field of view of the region would have an influence on \(\sigma^2\pos\).
\citet{arthur2016turbulence} compared multiple studies of the
inner Orion Nebula, finding agreement to within 20\%
in \(\sigma^2\pos\) determinations
for emission lines that trace the bulk of the fully ionized gas.

### 2022-12-20 table-fit-parameters.tex
Javier changes before submission

\begin{table*}
\begin{center}\caption{Fitting parameters.}
\begin{tabular}{cCCCCCCCC}\toprule
\hii{}    &  \text{No. merged} & \text{Relatively}  & \text{Weight / No. points}     &  \text{Weight / No. points}     & \text{Max.}  & \text{Reduced} & \text{Autocorrelation } & \text{Acceptance}\\
Region    &  \text{points} & \text{uncertainty} & \text{Small scales} &  \text{Large scales} & \text{separation}  & \text{chi-square} & \text{time} & \text{fraction}\\
\midrule
Orion     & - & 0.02    &  -           &   -        & 0.5  & 0.82 & 60  & 0.55\\
EON       & - & 0.025   &  2.0 / 3     &   -        & 0.5  & 0.70 & 527 & 0.45\\
Lagoon    & 2 & 0.08    &  2.5 / 16    &   2.5 / 8  & 0.5  & 0.94 & 70  & 0.49\\
Carina    & 2 & 0.055   &  3.0 / 14    &   3.0 / 4  & 0.5  & 0.94 & 72  & 0.50\\
30 Dor    & 5 &  0.07   &  -           &   -        & 0.9  & 0.98 & 82  & 0.54\\
NGC 346   & 3 & 0.04    &  -           &   -        & 0.8  & 0.83 & 76  & 0.51\\
Hubble V  & - & 0.05    &  2.0 / 3     &   -        & 0.6  & 0.86 & 440 & 0.44\\
Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5  & 0.73 & 83  & 0.49\\
NGC 595   & - &  0.055  &  4.5 / 3     &   3.0 / 5  & 0.5  & 0.83 & 63  & 0.51\\
NGC 604   & - &  0.095  &   2.5 / 3    &   1.25 / 2 & 0.5  & 0.71 & 124 & 0.44\\
\bottomrule
\end{tabular}\label{tab:fitting-parameters}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}\caption{Fitting parameters.}
\begin{tabular}{cCCCCCCCC}\toprule
\hii{}    &  \text{No. points} & \text{Relatively}  & \text{Weight / No. points}     &  \text{Weight / No. points}     & \text{Max.}  & \text{Reduced} & \text{Autocorrelation } & \text{Acceptance}\\
Region    &  \text{merged} & \text{uncertainty} & \text{Small scales} &  \text{Large scales} & \text{separation}  & \text{chi-square} & \text{time} & \text{fraction}\\
\midrule
Orion     & 3 & 0.02    &  -           &   -        & 0.5L  & 0.82 & 60  & 0.55\\
EON       & - & 0.03   &  2.0 / 3     &   3.0 / 3        & 0.7L  & 0.62 & 40 & 0.64\\
Lagoon    & 2 & 0.08    &  2.5 / 16    &   2.5 / 8  & 0.5L  & 0.94 & 72  & 0.50\\
Carina    & 2 & 0.055   &  3.0 / 14    &   3.0 / 4  & 0.5L  & 0.94 & 72  & 0.50\\
30 Dor    & 5 &  0.07   &  -           &   -        & 0.9L  & 0.98 & 84  & 0.54\\
NGC 346   & 3 & 0.02    &  -           &   -        & 0.5L  & 0.83 & 64  & 0.54\\
Hubble V  & - & 0.05    &  2.0 / 3     &   -        & 0.6L  & 0.86 & 340 & 0.44\\
Hubble X  & - & 0.032   &  2.0 / 4     &   2.0 / 6  & 0.5L  & 0.73 & 79  & 0.49\\
NGC 595   & - &  0.055  &  4.5 / 3     &   3.0 / 5  & 0.5L  & 0.83 & 67  & 0.51\\
NGC 604   & - &  0.08  &   2.0 / 3    &   1.5 / 2 & 0.5L  & 0.92 & 112 & 0.45\\
\bottomrule
\end{tabular}\label{tab:fitting-parameters}
\end{center}
\end{table*}
